Deep Reinforcement Learning for Conservation Decisions

### 2022-01-31 manuscript/manuscript.Rmd

---
title: Deep Reinforcement Learning for Conservation Decisions
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: mlapeyro@berkeley.edu
  - name: Melissa S. Chapman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: mchapman@berkeley.edu
  - name: Kari E. A. Norman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: kari.norman@berkeley.edu
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu (corresponding author)
abstract: |
  Can machine learning help us make better decisions about a changing planet?
  In this paper, we illustrate and discuss the potential of a promising corner of machine learning known as _reinforcement learning_ (RL) to help tackle the most challenging conservation decision problems.
  RL is uniquely well suited to conservation and global change challenges for three reasons: 
  (1) RL explicitly focuses on designing an agent who _interacts_ with an environment which is dynamic and uncertain,
  (2) RL approaches do not require massive amounts of data, 
  (3) RL approaches would utilize rather than replace existing models, simulations, and the knowledge they contain.
  While this potential may be compelling, the challenges involved in successfully deploying RL-based management to realistic scenarios are formidable --
  the required expertise and computational cost may place these applications beyond the reach of all but international technology firms.
  Ecologists must establish a better understanding of how these algorithms work and fail if we are to realize this potential and avoid the pitfalls such a transition would bring.
  To this end, we provide a conceptual and technical introduction to RL and its relevance to ecological and conservation challenges, including examples of a problem in setting fisheries quotas and in managing ecological tipping points.
  Four appendices with annotated code provide a tangible introduction to researchers looking to adopt, evaluate, or extend these approaches.

>>>>

---
title: Deep Reinforcement Learning for Conservation Decisions
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: mlapeyro@berkeley.edu
  - name: Melissa S. Chapman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: mchapman@berkeley.edu
  - name: Kari E. A. Norman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: kari.norman@berkeley.edu
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu (corresponding author)
abstract: |
  Can machine learning help us make better decisions about a changing planet?
  In this paper, we illustrate and discuss the potential of a promising corner of machine learning known as _reinforcement learning_ (RL) to help tackle the most challenging conservation decision problems.
  RL is uniquely well suited to conservation and global change challenges for three reasons: 
  (1) RL explicitly focuses on designing an agent who _interacts_ with an environment which is dynamic and uncertain,
  (2) RL approaches do not require massive amounts of data, 
  (3) RL approaches would utilize rather than replace existing models, simulations, and the knowledge they contain.
  While this potential may be compelling, the challenges involved in successfully deploying RL-based management to realistic scenarios are formidable --
  the required expertise and computational cost may place these applications beyond the reach of all but large, international technology firms.
  Ecologists must establish a better understanding of how these algorithms work and fail if we are to realize this potential and avoid the pitfalls such a transition would bring.
  To this end, we provide a conceptual and technical introduction to RL and its relevance to ecological and conservation challenges, including examples of a problem in setting fisheries quotas and in managing ecological tipping points.
  Four appendices with annotated code provide a tangible introduction to researchers looking to adopt, evaluate, or extend these approaches.
